### 2015-10-14 paper.tex
Add citation for dataset
Minor edits

The present task was to acquire a new dataset for the lower solidity RM2
turbine, but at higher Reynolds numbers than those achieved in the experiments
at SAFL. It is also suspected that the strut drag model in CACTUS could be the
source of some discrepancy. The strut drag was deliberately modified in the
physical model to provide data to help answer that question. This dataset is
publicly available for both validation of CACTUS and other numerical models.

@@

A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
parameters were scaled from the RM2 ``rev 0'' design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
shaft \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

>>>>

The present task was to acquire a new dataset for the lower solidity RM2
turbine, but at higher Reynolds numbers than those achieved in the experiments
at SAFL. It is also suspected that the strut drag model in CACTUS could be the
source of some discrepancy. The strut drag was deliberately modified in the
physical model to provide data to help answer that question. This dataset is
publicly available for both validation of CACTUS and other numerical models
\cite{Bachant2015-RM2-data}.

@@

A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
parameters were scaled from the RM2 ``rev 0'' design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
model \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.
